Pillar 1 - Sequential Pattern Mining

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
Use purrr to simplify the code d_transcript_cum
reduced code length by half

  # item_take
  mutate(
    item_take = paste(item, "take", sep = "_")
  ) %>%

  # course current
  group_by(
    sequenceID,
    eventID
    ) %>%
  summarize_at(
    c("item", "item_take", "item_PF", "item_HL"),
    function(x) list(unique(x))
    ) %>%

  # course current all
  rowwise %>%
  mutate(
    course_current = list(c(item, item_take, item_PF, item_HL))
    ) %>%

  # course past
  group_by(
    sequenceID
    ) %>%
  mutate(
    course_past = Reduce(
      f = c,
      x = course_current,
      accumulate = TRUE
      ) %>%
      lag(
        default = as.character(NA)
        )
    ) %>%

  # course so far, course not so far
  rowwise %>%
  mutate(

    course_past_current = list(union  (course_past, course_current      )),

    course_not_yet      = list(setdiff(course_all , course_past_current )),
    course_not_yet      = list(paste(course_not_yet, "not", sep = "_"   )),

    course_so_far       = list(union  (course_past, course_not_yet))

    ) %>%
  ungroup %>%

  # lhs: past, rhs: present
  select(
    lhs = course_so_far,
    rhs = course_current
  )
```

>>>>

  # item_take
  mutate(item_take = paste_(item, "take")) %>%

  # current courses
  group_by(sequenceID, eventID) %>%

  summarize_at(vars(matches("item")), ~ unique(.) %>% list) %>%

  mutate(course_current = list(item, item_take, item_PF, item_HL) %>% pmap(~ c(...) %>% unique)) %>%

  # courses so far, past courses and course not taken yet
  group_by(sequenceID) %>%

  arrange(eventID) %>%

  mutate(
    course_so_far  = course_current %>% accumulate(union),
    course_past    = course_so_far  %>% lag(default = NA_character_),
    course_not_yet = course_past    %>% map(~ setdiff(course_all, .) %>% paste_("not"))
    ) %>%

  ungroup %>%

  # lhs: past courses and courses not taken yet, rhs: current courses
  mutate(
    lhs = list(course_past, course_not_yet) %>% pmap(union),
    rhs = course_current
    )
```
